---
title: Integrating Python into your R code with reticulate
author: Your Name
date: '2018-03-27'
slug: integrating-python-into-your-r-code-with-reticulate
categories:
  - Coding
tags:
  - R
  - R packages
  - reticulate
  - Python
menu: "main"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The recent introduction of the R package [reticulate](https://github.com/rstudio/reticulate) now allows for the seemless integration of Python coding into an R workflow. Here I'll provide a very simple, quick example using `reticulate` in an RMarkdown document within RStudio, for further detail see https://github.com/rstudio/reticulate#python-in-r-markdown.

## Setting up

Install the reticulate package:
```{r, eval=FALSE}
install.packages('reticulate')
```

## Running Python within an R chunk

We can now directly import packages within an R chunk in RMarkdown:
```{r, warning=FALSE, message=FALSE}
require(reticulate) # load reticulate package
os <- import("os")  # import os
os$listdir(".")     # use listdir function of os to list the contents of current dir
```

## Running Python within a Python chunk

Can evaluate python within a chunk:
```{python}
import numpy as np
t = np.arange(0.0, 2.0, 0.01)
s = 1 + np.sin(2*np.pi*t)
print(s)
```
