---
title: Creating 'pretty' tables using RMarkdown
author: Miles Benton
date: '2018-01-25'
slug: creating-pretty-tables-using-rmarkdown
categories:
  - Administration
  - Coding
tags:
  - R packages
  - Rmarkdown
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# library(printr)
library(knitr)
library(kableExtra)
options(knitr.table.format = 'markdown')
```

Obviously R is capable of outputting data in various formats. The default method is functional but not 'pretty':

```{r}
dt <- mtcars[1:5, 1:6]
dt
```

Now what happens if we use the `kable()` function from `knitr`:

```{r}
kable(dt)
```

That's looking better but we can provide more parameters to tweak the output:

```{r}
dt %>% 
  kable("html", caption = 'This is a table with a caption', digits = 2, align = 'c') %>% 
  kable_styling(font_size = 14)
```


### Interactive tables

I will cover interactive tables generated using `htmltools` and the `DT` package at a later date.


#### Note:

I've added custom CSS to format the tables:
```css
<style type="text/css">
th {
  background-color:#b1b1b1;
  border-top:1px solid black;
  border-bottom:1px solid black;
  padding:12px;}

td{
  background-color:#e7e7e7;
	border-bottom:1px dotted black;
	padding:2px;}

table{ 
  border-collapse:collapse;
	margin:10px 150px
	border: 1px solid black;}
</style>
```